\thetitle

### 2022-04-15 paper/paper.tex
Add greedy algorithm and simulated annealing Use oneunit(T) instead of T(1) et sim Replace constant UIntTypes vector with function of same purpose
small improvement to binary search add plot for simulated annealing, begin writeup

\ifen
\newcommand{\thetitle}{How to apply to college}
\newcommand{\therunningtitle}{\thetitle}
\newcommand{\thedate}{\today}
\newcommand{\theauthor}{Max Kapur}
\else
\newcommand{\thetitle}{대학 지원 최적화 문제}
\newcommand{\therunningtitle}{\thetitle}
\newcommand{\thedate}{\today}
\newcommand{\theauthor}{Max Kapur}
\fi

@@

\ifen 
An intuitive extension of the greedy algorithm for Alma's problem is to iteratively add to $\mathcal{X}$ the school $k$ for which $\bigl( v(\mathcal{X}\cup\{k\}) - v(\mathcal{X}) \bigr) / g_k$ is largest. However, the construction above shows that the objective function of Ellis's problem can approximate that of a knapsack problem with arbitrary precision. Therefore, in pathological examples such as the following, the greedy algorithm can achieve an arbitrarily small approximation ratio. 
\else
알마 문제를 위한 탐욕 해법의 직관적인 확장은 $\bigl( v(\mathcal{X}\cup\{k\}) - v(\mathcal{X}) \bigr) / g_k$-값이 가장 큰 학교 $k$를  $\mathcal{X}$에 차례대로 추가하는 것이다. 그러나 위에서 도출한 변환은 엘리스 문제의 목적함수를 배낭 문제의 목적함수의 원하는 만큼 정확한 근사로 만들 수 있음을 의미한다. 따라서 다음 같은 병례에서 탐욕 해법은 임의로 낮은 근사 비율을 일으킬 수 있다.
\fi
\begin{example}
\ifen
Let $t = (10, 2021)$, $f = (1, 1)$, $g = (1, 500)$, and $H = 500$. Then the greedy approximation algorithm produces the clearly inoptimal solution $\mathcal{X} = \{1\}$. 
\else
 $t = (10, 2021)$, $f = (1, 1)$, $g = (1, 500)$, 그리고 $H = 500$이라고 하자. 그러면 탐욕 해법은 $\mathcal{X} = \{1\}$을 출력하며 이는 분명히 최적해가 아니다.
\fi
\end{example} 
\ifen
We might expect to obtain a better approximate solution to Ellis's problem by solving the following knapsack problem (nevermind that it is NP-complete) as a surrogate.
\begin{equation}
\text{maximize}\quad \sum_{j \in \mathcal{X}} f_j t_j \qquad \text{subject to}\quad\mathcal{X}\subseteq\mathcal{C},~~\sum_{j \in \mathcal{X}} g_j \leq H
\end{equation}
However, upon inspection, this solution merely generalizes the na\"ive algorithm for Alma's problem (Definition \ref{naivealgorithm}). In Ellis's problem, because the number of schools in the optimal portfolio can be as large as $m-1$, the knapsack solution's approximation coefficient is $1/(m-1)$ by analogy with \eqref{oneoverhopt}. A tight example is as follows. 
\else
엘리스 문제의 좀 더 좋은 근사해를 찾기 위해 다음 배낭 문제를 (NP-complete함을 무시하고) 대리 문제로 푸는 것에 매력은 있다.
\begin{equation}
\text{maximize}\quad \sum_{j \in \mathcal{X}} f_j t_j \qquad \text{subject to}\quad\mathcal{X}\subseteq\mathcal{C},~~\sum_{j \in \mathcal{X}} g_j \leq H
\end{equation}
그러나 이러한 해법은 사실 알마 문제의 나이브 해법(정의 \ref{naivealgorithm})의 단순한 일반화임을 알 수 있다. 엘리스 문제에서 최적 포트폴리오에 크기가 $m-1$이 될 수 있으므로 배낭 문제 해법의 근사 계수는 \eqref{oneoverhopt}과(와) 유사하듯이 $1 / (m-1)$이다. 타이트한 예는 다음과 같다.
\fi
\begin{example}
\ifen Consider the following instance of Ellis's problem, where $H = m-1$.
\else 엘리스 문제의 다음 인스턴스를 고려하자. 단, $H = m-1$이다. \fi
\begin{center}
\begin{tabular}{r|cccc}
$j$   & $1$            & $\cdots$ & $m-1$          & $m$            \\ \hline
$f_j$ & $1$            &  $\cdots$ & $1$            & $\frac{1}{m-1}$ \\
$t_j$ & $\frac{1}{m-1}$ &  $\cdots$ & $\frac{1}{m-1}$ & $m-1$          \\
$g_j$ & $1$            &  $\cdots$ & $1$            & $m-1$         
\end{tabular}%
\end{center}
\ifen
The feasible solutions $\mathcal{Y} = \{1, \dots, m-1\}$ and $\mathcal{X} = \{ m\}$ each have $\sum_{j \in \mathcal{Y}} f_j t_j = \sum_{j \in \mathcal{X}} f_j t_j =  1$, and thus the knapsack algorithm can choose $\mathcal{Y}$ with $v(\mathcal{Y}) = 1/(m-1)$. But the optimal solution is  $\mathcal{X}$ with $v(\mathcal{X}) =  1$. 
\else
가능해 $\mathcal{Y} = \{1, \dots, m-1\}$와 $\mathcal{X} = \{ m\}$에 대해 $\sum_{j \in \mathcal{Y}} f_j t_j = \sum_{j \in \mathcal{X}} f_j t_j =  1$이므로 배낭 문제 해법은  $\mathcal{Y}$를 선택할 수 있다. 그의 가치는 $v(\mathcal{Y}) = 1/(m-1)$이다. 그러나 $\mathcal{X}$는 최적해이며 그의 가치는 $v(\mathcal{X}) =  1$이다.
\fi
\end{example}

@@

\ifen
The branch-and-bound algorithm is an interesting benchmark, but as a kind of enumeration algorithm, its computation time grows rapidly in the problem size, and unlike the approximation scheme we propose later on, there is no guaranteed bound on the approximation error after a fixed number of iterations. Moreover, when there are many schools in $\mathcal{N}$, the LP upper bound may be much higher than $v_{\mathcal{I}}[n']$. This means that significant fathoming operations do not occur until the algorithm has explored deep into the tree, at which point the bulk of the computational effort has already been exhausted. In our numerical experiments, Algorithm \ref{ellisbnb} was ineffective on instances larger than about $m=35$ schools, and therefore it does not represent a significant improvement over na\"ive enumeration. 
\else
분지한계법은 기술적으로 유리한 기준점이지만, 일종의 열거 해법이므로 계산 시간이 문제 크기와 지수적으로 늘어난다. 그리고 뒤에서 제안하는 근사 해법과 달리, 주어진 반복한계의 개수에 대한 정확성 보장이 없다. 또한 $\mathcal{N}$에 학교가 많을 때, 선형 완화 문제 상한은 $v_{\mathcal{I}}[n']$보다 매우 높을 수도 있다. 이는 해법이 나무에 어느 정도 깊게 파고들어야 마디를 제외할 수 있음을 의미하며, 그때 계산 노력의 대부분은 이미 쏟은 것이다. 수리 실험에서, 알고리즘 \ref{ellisbnb}은(는) 약 $m=35$개의 학교를 넘는 인스턴스에 대해 비효율적이었으며 이는 단순한 열거법에 비해 큰 개선이 아니다.
\fi

@@

\ifen
\begin{algorithm}[h] 
%\DontPrintSemicolon
\caption{Fully polynomial-time approximation scheme for Ellis's problem.} \label{ellisDP3}
\KwData{Utility values $t \in \mathbb{N}^m$, admissions probabilities $f \in (0, 1]^m$, application costs $g \in (0, \infty)^m$, budget $H \in (0, \infty)^m$, tolerance $\varepsilon \in (0, 1)$.}
Index schools in ascending order by $t$\;
Set precision $P \gets \bigl\lceil\log_{10}\left(m^2 / \varepsilon \bar U\right)\bigr\rceil$\;
%\SetKwProg{Fn}{function}{ do}{end}
%\Fn{$G(j, v)$}{
%	\lIf{$v \leq 0$}{\Return{$0$}}
%	\lElseIf{$j=0$ or $t_j < v$}{\Return{$\infty$}}
%	\lElse {\Return{$\min\bigl\{ G(j-1, v), g_j + G\bigl(j-1, v -  \Delta_j(v)\bigr) \bigr\}$}}
%}
Fill a lookup table with the entries of $G[j, h]$\; \label{createdlookuptable}
$v\gets  \max\{ w \in \mathcal{V} : G[m, w] \leq H\}$\; \label{vrecordedhere}
$\mathcal{X} \gets \O$\;
\For{$j = m, m-1, \dots, 1$}{
	\If{$G[j, v]< \infty$ and $G[j, v] < G[j-1, v]$}{
		$\mathcal{X} \gets \mathcal{X}\cup\{j\}$\; 
		$v \gets v -  \Delta_j(v)$\;
	}
}
\Return{$\mathcal{X}$}
\end{algorithm}
\else
\begin{algorithm}[h] 
%\DontPrintSemicolon
\caption{엘리스의 문제를 위한 완전 다항 시간 근사 해법.} \label{ellisDP3}
\KwData{효용 모수 $t \in \mathbb{N}^m$, 합격 확률 $f \in (0, 1]^m$, 지원 비용 $g \in (0, \infty)^m$, 예산 $H \in (0, \infty)^m$, 허용치 $\varepsilon \in (0, 1)$.}
$t$의 순서대로 학교를 배열한다\;
정확도 $P \gets \bigl\lceil\log_{10}\left(m^2 / \varepsilon \bar U\right)\bigr\rceil$\;
%\SetKwProg{Fn}{function}{ do}{end}
%\Fn{$G(j, v)$}{
%	\lIf{$v \leq 0$}{\Return{$0$}}
%	\lElseIf{$j=0$ or $t_j < v$}{\Return{$\infty$}}
%	\lElse {\Return{$\min\bigl\{ G(j-1, v), g_j + G\bigl(j-1, v -  \Delta_j(v)\bigr) \bigr\}$}}
%}
$G[j, h]$의 값으로 표를 채운다\; \label{createdlookuptable}
$v\gets  \max\{ w \in \mathcal{V} : G[m, w] \leq H\}$\; \label{vrecordedhere}
$\mathcal{X} \gets \O$\;
\For{$j = m, m-1, \dots, 1$}{
	\If{$G[j, v]< \infty$이고 $G[j, v] < G[j-1, v]$}{
		$\mathcal{X} \gets \mathcal{X}\cup\{j\}$\; 
		$v \gets v -  \Delta_j(v)$\;
	}
}
\Return{$\mathcal{X}$}
\end{algorithm}
\fi

@@

@@

\ifen \subsection{Experimental procedure} \else \subsection{실험 방법}\fi
\def\nmarkets{50}
\ifen
The experimental procedure was as follows. First, to generate synthetic markets, we drew the $t_j$-values independently from an exponential distribution with a scale parameter of ten and rounded up to the nearest integer. To achieve partial negative correlation between $t_j$ and $f_j$, we then set $f_j = 1 / (t_j + 10\,Q)$, where $Q$ is drawn uniformly from the interval $[0, 1)$. In the first experiment, which concerns Alma's problem, we set each $g_j = 1$ and $H = h = \lfloor m/ 2 \rfloor$. In the second experiment, which concerns Ellis's problem, each $g_j$ is drawn uniformly from the set $\{5, \dots, 10\}$ and we set $H = \lfloor \frac{1}{2} \sum g_j \rfloor$. This cost distribution resembles real-world college application fees, which are often multiples of \$10 between \$50 and \$100. A typical instance is shown in Figure \ref{samplemarket}.
\else
실험 방법은 다음과 같다. 먼저, 가산 시장을 생성하기 위해 $t_j$-값을 평균이 10인 지수 분포에서 독립적으로 관측하고 정수로 올림했다. 그다음에, $t_j$와 $f_j$가 서로 부분적으로 반비례하게 만들도록 $f_j = 1 / (t_j + 10\,Q)$로 정의했다. 단, $Q$는 $[0, 1)$에서 균일한 확률로 관측한다. 알마의 문제를 고려하는 첫 번째 실험에서, 모든 $g_j = 1$ 그리고 $H = h = \lfloor m/ 2 \rfloor$으로 처리했다. 엘리스의 문제를 고려하는 두 번째 실험에서, 모든  $g_j$를 $\{5, \dots, 10\}$에서 균일한 확률로 관측했으며 $H = \lfloor \frac{1}{2} \sum g_j \rfloor$으로 처리했다. 실제 대학 지원 비용인 50과 100달러 사이에 10달러의 어떤 배수이므로 합리적인 비용 분포이다. 그림 \ref{samplemarket}에서 전형적인 인스턴스가 나타난다.
\fi

\ifen
The experimental variables were the market size $m$, the choice of algorithm, and (for Algorithm \ref{ellisDP3}) the tolerance $\varepsilon$. For each combination of the experimental variables, we generated \nmarkets~markets, and the optimal portfolio was computed three times, with the fastest of the three repetitions recorded as the computation time. We then report the mean and standard deviation across the \nmarkets~markets. Therefore, each cell of each table below represents a statistic over {\the\numexpr 3 * \nmarkets \relax}~computations. Where applicable, we do not count the time required to sort the entries of $t$.
\else
실험 변수로는 시장의 크기 $m$, 해법 선택, 그리고 (알고리즘 \ref{ellisDP3}인 경우) 허용치 $\varepsilon$을 고려했다. 실험 변수의 각 조합에 대해,  \nmarkets 개의 시장을 생성했으며 최적 포트폴리오를 3번 계산 한 것 중 가장 빠른 것으로 계산 시간으로 기록했다. \nmarkets 개의 시장에 대한 평균과 평균편차를 표에 나타낸다. 따라서 아래 표의 각 칸은 {\the\numexpr 3 * \nmarkets \relax}개의 계산에 대한 통계다. $t$를 배열하는 시간은 고려하지 않았다.
\fi

\ifen \subsection{Summary of results} \else \subsection{결과 정리}\fi
\ifen
In our first experiment, we compare the performance of Algorithm \ref{algorithmforlargeh} for homogeneous-cost markets of various sizes when the set of candidate schools $\mathcal{C}$ is stored as a list and as a binary max heap ordered by the $f_j \bar t_j$-values. The results appear in Table \ref{experiment1results}. Our results indicate that the list implementation is faster. %However, the ratio between the average times of the two implementations stays roughly constant, suggesting that a more effective heap implementation could be competitive in certain classes of problem instances. Overall, the rate of growth is quadratic in $m$, which accords with the $O(hm)$ time complexity result of Theorem \ref{validityofalmaalgorithm}.
\else
첫 번째 실험에서, 동일한 지원 비용으로 정의된 크기가 다양한 시장에 대해 알고리즘 \ref{algorithmforlargeh}의 성능을 고려했다. 이를 $\mathcal{C}$를 목록 혹은 $f_j \bar t_j$-값에 따라 배열된 힙 구현으로 구성하는 경우로 나눴으며 실험 결과는 표 \ref{experiment1results}에서 등장한다. 실험 결과에 따라 목록 구현이 더 빠른 해법이었다. %그러나, 두개의 방법 사이에 계산 시간 비율은 거의 상수이므로 개선된 힙 해법이 어떤 문제 인스턴스에 대해 더 빠를 가능성이 있어 보인다. 전체적으로 계산 시간은 $m$의 제곱으로 늘아나며 이는 정리 \ref{validityofalmaalgorithm}에서 말한 $O(hm)$-시간과 동의한다.
\fi

@@

\ifen
In the second experiment, we turn to the general problem, and compare the performance of the exact algorithms (Algorithms \ref{ellisbnb} and \ref{ellisDP1}) and the approximation scheme (Algorithm \ref{ellisDP3}) at tolerances 0.5 and 0.05.  The results, which appear in Table \ref{experiment2results}, broadly agree with the time complexity analyses presented above. The branch-and-bound algorithm proved impractical for even medium-sized instances. Overall, we found the exact dynamic program to be the fastest algorithm, while the FPTAS was rather slow, a result that echoes the results of computational studies on knapsack problems (Martello and Toth 1990, \S\,2.10).

>>>>

\ifen
\newcommand{\thetitle}{The College Application Problem}
\newcommand{\therunningtitle}{\thetitle}
\newcommand{\thedate}{\today}
\newcommand{\theauthor}{Max Kapur}
\else
\newcommand{\thetitle}{대학 지원 최적화 문제}
\newcommand{\therunningtitle}{\thetitle}
\newcommand{\thedate}{\today}
\newcommand{\theauthor}{Max Kapur}
\fi

@@

\ifen 
An intuitive extension of the greedy algorithm for Alma's problem is to iteratively add to $\mathcal{X}$ the school $k$ for which $\bigl( v(\mathcal{X}\cup\{k\}) - v(\mathcal{X}) \bigr) / g_k$ is largest. However, the construction above shows that the objective function of Ellis's problem can approximate that of a knapsack problem with arbitrary precision. Therefore, in pathological examples such as the following, the greedy algorithm can achieve an arbitrarily small approximation ratio. 
\else
알마 문제를 위한 탐욕 해법의 직관적인 확장은 $\bigl( v(\mathcal{X}\cup\{k\}) - v(\mathcal{X}) \bigr) / g_k$-값이 가장 큰 학교 $k$를  $\mathcal{X}$에 차례대로 추가하는 것이다. 그러나 위에서 도출한 변환은 엘리스 문제의 목적함수를 배낭 문제의 목적함수의 원하는 만큼 정확한 근사로 만들 수 있음을 의미한다. 따라서 다음 같은 병례에서 탐욕 해법은 임의로 낮은 근사 비율을 일으킬 수 있다.
\fi
\begin{example}
\ifen
Let $t = (10, 2021)$, $f = (1, 1)$, $g = (1, 500)$, and $H = 500$. Then the greedy approximation algorithm produces the clearly inoptimal solution $\mathcal{X} = \{1\}$. 
\else
 $t = (10, 2021)$, $f = (1, 1)$, $g = (1, 500)$, 그리고 $H = 500$이라고 하자. 그러면 탐욕 해법은 $\mathcal{X} = \{1\}$을 출력하며 이는 분명히 최적해가 아니다.
\fi
\end{example} 
\ifen
We might expect to obtain a better approximate solution to Ellis's problem by solving the following knapsack problem (nevermind that it is NP-complete) as a surrogate.
\begin{equation}
\text{maximize}\quad \sum_{j \in \mathcal{X}} f_j t_j \qquad \text{subject to}\quad\mathcal{X}\subseteq\mathcal{C},~~\sum_{j \in \mathcal{X}} g_j \leq H
\end{equation}
However, upon inspection, this solution merely generalizes the na\"ive algorithm for Alma's problem (Definition \ref{naivealgorithm}). In Ellis's problem, because the number of schools in the optimal portfolio can be as large as $m-1$, the knapsack solution's approximation coefficient is $1/(m-1)$ by analogy with \eqref{oneoverhopt}. A tight example is as follows. 
\else
엘리스 문제의 좀 더 좋은 근사해를 찾기 위해 다음 배낭 문제를 (NP-complete함을 무시하고) 대리 문제로 푸는 것에 매력은 있다.
\begin{equation}
\text{maximize}\quad \sum_{j \in \mathcal{X}} f_j t_j \qquad \text{subject to}\quad\mathcal{X}\subseteq\mathcal{C},~~\sum_{j \in \mathcal{X}} g_j \leq H
\end{equation}
그러나 이러한 해법은 사실 알마 문제의 나이브 해법(정의 \ref{naivealgorithm})의 단순한 일반화임을 알 수 있다. 엘리스 문제에서 최적 포트폴리오에 크기가 $m-1$이 될 수 있으므로 배낭 문제 해법의 근사 계수는 \eqref{oneoverhopt}과(와) 유사하듯이 $1 / (m-1)$이다. 타이트한 예는 다음과 같다.
\fi
\begin{example} \label{knapsackheuristicellis}
\ifen Consider the following instance of Ellis's problem, where $H = m-1$.
\else 엘리스 문제의 다음 인스턴스를 고려하자. 단, $H = m-1$이다. \fi
\begin{center}
\begin{tabular}{r|cccc}
$j$   & $1$            & $\cdots$ & $m-1$          & $m$            \\ \hline
$f_j$ & $1$            &  $\cdots$ & $1$            & $\frac{1}{m-1}$ \\
$t_j$ & $\frac{1}{m-1}$ &  $\cdots$ & $\frac{1}{m-1}$ & $m-1$          \\
$g_j$ & $1$            &  $\cdots$ & $1$            & $m-1$         
\end{tabular}%
\end{center}
\ifen
The feasible solutions $\mathcal{Y} = \{1, \dots, m-1\}$ and $\mathcal{X} = \{ m\}$ each have $\sum_{j \in \mathcal{Y}} f_j t_j = \sum_{j \in \mathcal{X}} f_j t_j =  1$, and thus the knapsack algorithm can choose $\mathcal{Y}$ with $v(\mathcal{Y}) = 1/(m-1)$. But the optimal solution is  $\mathcal{X}$ with $v(\mathcal{X}) =  1$. 
\else
가능해 $\mathcal{Y} = \{1, \dots, m-1\}$와 $\mathcal{X} = \{ m\}$에 대해 $\sum_{j \in \mathcal{Y}} f_j t_j = \sum_{j \in \mathcal{X}} f_j t_j =  1$이므로 배낭 문제 해법은  $\mathcal{Y}$를 선택할 수 있다. 그의 가치는 $v(\mathcal{Y}) = 1/(m-1)$이다. 그러나 $\mathcal{X}$는 최적해이며 그의 가치는 $v(\mathcal{X}) =  1$이다.
\fi
\end{example}

@@

\ifen
The branch-and-bound algorithm is an interesting benchmark, but as a kind of enumeration algorithm, its computation time grows rapidly in the problem size, and unlike the approximation scheme we propose later on, there is no guaranteed bound on the approximation error after a fixed number of iterations. Moreover, when there are many schools in $\mathcal{N}$, the LP upper bound may be much higher than $v_{\mathcal{I}}[n']$. This means that significant fathoming operations do not occur until the algorithm has explored deep into the tree, at which point the bulk of the computational effort has already been exhausted. In our numerical experiments, Algorithm \ref{ellisbnb} was ineffective on instances larger than about $m=35$ schools, and therefore it does not represent a significant improvement over na\"ive enumeration. We speculate that the algorithm can be improved by incorporating cover inequalities (Wolsey 1998, \S\,9.3).  
\else
분지한계법은 기술적으로 유리한 기준점이지만, 일종의 열거 해법이므로 계산 시간이 문제 크기와 지수적으로 늘어난다. 그리고 뒤에서 제안하는 근사 해법과 달리, 주어진 반복한계의 개수에 대한 정확성 보장이 없다. 또한 $\mathcal{N}$에 학교가 많을 때, 선형 완화 문제 상한은 $v_{\mathcal{I}}[n']$보다 매우 높을 수도 있다. 이는 해법이 나무에 어느 정도 깊게 파고들어야 마디를 제외할 수 있음을 의미하며, 그때 계산 노력의 대부분은 이미 쏟은 것이다. 수리 실험에서, 알고리즘 \ref{ellisbnb}은(는) 약 $m=35$개의 학교를 넘는 인스턴스에 대해 비효율적이었으며 이는 단순한 열거법에 비해 큰 개선이 아니다. 하지만, 커버 부등식을 도입하여 해법을 개선할 가능성이 보인다 (Wolsey 1998, \S\,9.3).
\fi

@@

\ifen
\begin{algorithm}[h] 
%\DontPrintSemicolon
\caption{Fully polynomial-time approximation scheme for Ellis's problem.} \label{ellisDP3}
\KwData{Utility values $t \in  (0, \infty)^m$, admissions probabilities $f \in (0, 1]^m$, application costs $g \in (0, \infty)^m$, budget $H \in (0, \infty)^m$, tolerance $\varepsilon \in (0, 1)$.}
Index schools in ascending order by $t$\;
Set precision $P \gets \bigl\lceil\log_{10}\left(m^2 / \varepsilon \bar U\right)\bigr\rceil$\;
%\SetKwProg{Fn}{function}{ do}{end}
%\Fn{$G(j, v)$}{
%	\lIf{$v \leq 0$}{\Return{$0$}}
%	\lElseIf{$j=0$ or $t_j < v$}{\Return{$\infty$}}
%	\lElse {\Return{$\min\bigl\{ G(j-1, v), g_j + G\bigl(j-1, v -  \Delta_j(v)\bigr) \bigr\}$}}
%}
Fill a lookup table with the entries of $G[j, h]$\; \label{createdlookuptable}
$v\gets  \max\{ w \in \mathcal{V} : G[m, w] \leq H\}$\; \label{vrecordedhere}
$\mathcal{X} \gets \O$\;
\For{$j = m, m-1, \dots, 1$}{
	\If{$G[j, v]< \infty$ and $G[j, v] < G[j-1, v]$}{
		$\mathcal{X} \gets \mathcal{X}\cup\{j\}$\; 
		$v \gets v -  \Delta_j(v)$\;
	}
}
\Return{$\mathcal{X}$}
\end{algorithm}
\else
\begin{algorithm}[h] 
%\DontPrintSemicolon
\caption{엘리스의 문제를 위한 완전 다항 시간 근사 해법.} \label{ellisDP3}
\KwData{효용 모수 $t \in  (0, \infty)}^m$, 합격 확률 $f \in (0, 1]^m$, 지원 비용 $g \in (0, \infty)^m$, 예산 $H \in (0, \infty)^m$, 허용치 $\varepsilon \in (0, 1)$.}
$t$의 순서대로 학교를 배열한다\;
정확도 $P \gets \bigl\lceil\log_{10}\left(m^2 / \varepsilon \bar U\right)\bigr\rceil$\;
%\SetKwProg{Fn}{function}{ do}{end}
%\Fn{$G(j, v)$}{
%	\lIf{$v \leq 0$}{\Return{$0$}}
%	\lElseIf{$j=0$ or $t_j < v$}{\Return{$\infty$}}
%	\lElse {\Return{$\min\bigl\{ G(j-1, v), g_j + G\bigl(j-1, v -  \Delta_j(v)\bigr) \bigr\}$}}
%}
$G[j, h]$의 값으로 표를 채운다\; \label{createdlookuptable}
$v\gets  \max\{ w \in \mathcal{V} : G[m, w] \leq H\}$\; \label{vrecordedhere}
$\mathcal{X} \gets \O$\;
\For{$j = m, m-1, \dots, 1$}{
	\If{$G[j, v]< \infty$이고 $G[j, v] < G[j-1, v]$}{
		$\mathcal{X} \gets \mathcal{X}\cup\{j\}$\; 
		$v \gets v -  \Delta_j(v)$\;
	}
}
\Return{$\mathcal{X}$}
\end{algorithm}
\fi

@@

\ifen \subsection{Simulated annealing} \else \subsection{Simulated annealing}\fi\label{numericalexperiments}
Simulated annealing is a popular local-search technique for nonconvex optimization problems. Because of their inherent randomness, simulated-annealing algorithms offer no accuracy guarantee; however, they are easy to implement, computationally inexpensive, and often produce solutions with a small optimality gap. In this section, we present a simulated-annealing algorithm for Ellis's problem. It is based on the procedure for integer programs outlined by Wolsey (1998, \S\,12.3.2)

To generate an initial solution, our algorithm adopts the greedy heuristic of adding schools in descending order by $f_j t_j / g_j$ until the budget is exhausted. Example \ref{knapsackheuristicellis} shows that the approximation coefficient of this solution can be as low as $1 / (m-1)$; in typical instances, it is much higher. Given a solution $\mathcal{X}$, we generate a neighbor $\mathcal{X}_n$ by copying $\mathcal{X}$, adding schools to $\mathcal{X}_n$ until it becomes infeasible, then removing elements of $\mathcal{X}$ from $\mathcal{X}_n$ until feasibility is restored. If this increases the valuation of $\mathcal{X}$, then the candidate solution is updated to equal the neighbor; if not, then the candidate solution is updated with probability $\exp\bigl(v(\mathcal{X}_n) - v(\mathcal{X}) / T\bigr)$, where $T$ is a temperature parameter. This is repeated $N$ times, and the algorithm returns the best $\mathcal{X}$ observed.

\begin{algorithm}[h] 
%\DontPrintSemicolon
\caption{Simulated annealing for Ellis's problem.} \label{ellissimann}
\KwData{Utility values $t  (0, \infty)^m$, admissions probabilities $f \in (0, 1]^m$, application costs $g \in (0, \infty)^m$, budget $H \in (0, \infty)^m$, initial temperature $T > 0$, temperature reduction parameter $r \in (0, 1)$, number of iterations $N$.}
Add schools to $\mathcal{X}$ in descending order by $f_j t_j / g_j$ until the budget is exhausted\;
\For{$i = 1 \dots N$}{
	$\mathcal{X}_n \gets \operatorname{copy}(\mathcal{X})$\;
	Add random schools from $\mathcal{C} \setminus \mathcal{X}$ to $\mathcal{X}_n$ until  $\mathcal{X}_n$ infeasible\;
	Remove random schools in $\mathcal{X}$ from $\mathcal{X}_n$ until feasibility restored\;
	$\Delta = v(\mathcal{X}_n) - v(\mathcal{X})$\;
	\lIfElse{$\Delta \geq 0$}{$\mathcal{X} \gets \mathcal{X}_n$}
	{$\mathcal{X} \gets \mathcal{X}_n$ with probability $\exp(\Delta / T)$}
	$T \gets rT$\;
}
\Return{the best $\mathcal{X}$ found}
\end{algorithm}

\begin{proposition}
The computation time of Algorithm \ref{ellissimann} is $O(Nm)$. 
\end{proposition}

In our numerical experiments, the output of Algorithm \ref{ellissimann} was typically quite close to optimal.

%always within 10 percent of optimality.

@@

\ifen \subsection{Experimental procedure} \else \subsection{실험 방법}\fi
We conducted three numerical experiments. Experiments 1 and 2 evaluate the computation times of our algorithms for Alma's problem and Ellis's problem, respectively. Experiment 3 investigates the empirical accuracy of the simulated-annealing heuristic as compared to an exact algorithm.

\def\nmarkets{50}
\ifen
To generate synthetic markets, we drew the $t_j$-values independently from an exponential distribution with a scale parameter of ten and rounded up to the nearest integer. To achieve partial negative correlation between $t_j$ and $f_j$, we then set $f_j = 1 / (t_j + 10\,Q)$, where $Q$ is drawn uniformly from the interval $[0, 1)$. In Experiment 1, which concerns Alma's problem, we set $h = \lfloor m/ 2 \rfloor$. In Experiments 2 and 3, which concern Ellis's problem, each $g_j$ is drawn uniformly from the set $\{5, \dots, 10\}$ and we set $H = \lfloor \frac{1}{2} \sum g_j \rfloor$. This cost distribution resembles real-world college application fees, which are often multiples of \$10 between \$50 and \$100. A typical instance is shown in Figure \ref{samplemarket}.
\else
가산 시장을 생성하기 위해 $t_j$-값을 평균이 10인 지수 분포에서 독립적으로 관측하고 정수로 올림했다. 그다음에, $t_j$와 $f_j$가 서로 부분적으로 반비례하게 만들도록 $f_j = 1 / (t_j + 10\,Q)$로 정의했다. 단, $Q$는 $[0, 1)$에서 균일한 확률로 관측한다. 알마의 문제를 고려하는 실험 1에서, $h = \lfloor m/ 2 \rfloor$으로 처리했다. 엘리스의 문제를 고려하는 실험 2와 실험 3에서, 모든  $g_j$를 $\{5, \dots, 10\}$에서 균일한 확률로 관측했으며 $H = \lfloor \frac{1}{2} \sum g_j \rfloor$으로 처리했다. 실제 대학 지원 비용인 50과 100달러 사이에 10달러의 어떤 배수이므로 합리적인 비용 분포이다. 그림 \ref{samplemarket}에서 전형적인 인스턴스가 나타난다.
\fi

\ifen
The experimental variables in Experiments 1 and 2 were the market size $m$, the choice of algorithm, and (for Algorithm \ref{ellisDP3}) the tolerance $\varepsilon$. For each combination of the experimental variables, we generated \nmarkets~markets, and the optimal portfolio was computed three times, with the fastest of the three repetitions recorded as the computation time. We then report the mean and standard deviation across the \nmarkets~markets. Therefore, each cell of each table below represents a statistic over {\the\numexpr 3 * \nmarkets \relax}~computations. Where applicable, we do not count the time required to sort the entries of $t$. As the simulated annealing algorithm's computation time is negligible, it was excluded from Experiment 2. 
\else
실험 1과 실험 2의 실험 변수로는 시장의 크기 $m$, 해법 선택, 그리고 (알고리즘 \ref{ellisDP3}인 경우) 허용치 $\varepsilon$을 고려했다. 실험 변수의 각 조합에 대해,  \nmarkets 개의 시장을 생성했으며 최적 포트폴리오를 3번 계산 한 것 중 가장 빠른 것으로 계산 시간으로 기록했다. \nmarkets 개의 시장에 대한 평균과 평균편차를 표에 나타낸다. 따라서 아래 표의 각 칸은 {\the\numexpr 3 * \nmarkets \relax}개의 계산에 대한 통계다. $t$를 배열하는 시간은 고려하지 않았다. As the simulated annealing algorithm's computation time is negligible, it was excluded from Experiment 2. 
\fi

In Experiment 3, we generated 500 markets with sizes between $2^3$ and $2^11$ varying uniformly in the logarithm. For each market, we computed a heuristic solution using Algorithm \ref{ellissimann} and an exact solution using Algorithm \ref{ellisDP1} and calculated the optimality ratio.

\ifen \subsection{Summary of results} \else \subsection{결과 정리}\fi
\ifen
Experiment 1 compared the performance of Algorithm \ref{algorithmforlargeh} for homogeneous-cost markets of various sizes when the set of candidate schools $\mathcal{C}$ is stored as a list and as a binary max heap ordered by the $f_j \bar t_j$-values. The results appear in Table \ref{experiment1results}. Our results indicate that the list implementation is faster. %However, the ratio between the average times of the two implementations stays roughly constant, suggesting that a more effective heap implementation could be competitive in certain classes of problem instances. Overall, the rate of growth is quadratic in $m$, which accords with the $O(hm)$ time complexity result of Theorem \ref{validityofalmaalgorithm}.
\else
실험 1에서, 동일한 지원 비용으로 정의된 크기가 다양한 시장에 대해 알고리즘 \ref{algorithmforlargeh}의 성능을 고려했다. 이를 $\mathcal{C}$를 목록 혹은 $f_j \bar t_j$-값에 따라 배열된 힙 구현으로 구성하는 경우로 나눴으며 실험 결과는 표 \ref{experiment1results}에서 등장한다. 실험 결과에 따라 목록 구현이 더 빠른 해법이었다. %그러나, 두개의 방법 사이에 계산 시간 비율은 거의 상수이므로 개선된 힙 해법이 어떤 문제 인스턴스에 대해 더 빠를 가능성이 있어 보인다. 전체적으로 계산 시간은 $m$의 제곱으로 늘아나며 이는 정리 \ref{validityofalmaalgorithm}에서 말한 $O(hm)$-시간과 동의한다.
\fi

@@

\ifen
In Experiment 2, we turned to the general problem, and compared the performance of the exact algorithms (Algorithms \ref{ellisbnb} and \ref{ellisDP1}) and the approximation scheme (Algorithm \ref{ellisDP3}) at tolerances 0.5 and 0.05.  The results, which appear in Table \ref{experiment2results}, broadly agree with the time complexity analyses presented above. The branch-and-bound algorithm proved impractical for even medium-sized instances. Overall, we found the exact dynamic program to be the fastest algorithm, while the FPTAS was rather slow, a result that echoes the results of computational studies on knapsack problems (Martello and Toth 1990, \S\,2.10).
